% !TEX program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"
\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{multirow}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

% \name{Bin Yuan}

\basicInfo{
  \begin{tabu}{ c r r }
   \multirow{2}{1in}{\name{Zhao-Bing}}\hspace{6.5em} &  &  \\
    & \email{zhaobingcn@hotmail.com} & \pbar{Java}{0.8} \\
    & \phone{(+86) 182-2291-7001} & \pbar{C++}{0.5} \\
    & \github[github.com/zhaobingcn]{https://github.com/zhaobingcn} & \pbar{Python}{0.5} \\
    % & \github[github.com/billryan]{https://github.com/billryan} & \pbar{Javascript}{0.5}
  \end{tabu}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{ Beijing University of Post and Telecommunication (BUPT)}, Beijing, China}{2015 -- Present}
\textit{Master student} in Computer Science and Technology (CST), expected March 2018
\datedsubsection{\textbf{Tianjin Polytechnic University (TJPU)}, TianJin, China}{2011 -- 2015}
\textit{B.S.} in Software Engineering(SE)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{CETC ISA} Beijing, China}{2016.4 -- Present}
\role{Chinese Knowledge Graph Retrieval System}{Project development}
Brief introduction:A chinese knowledge graph project, my role is to use Neo4j to generate knowledge graph and accomplish information retrieval.
\begin{itemize}
  \item Achieved the storage of 100M entities and 1000M releationships' graph based on Neo4j.
  \item Used Neo4j, Spark GraphX, Lucene, Spring, Spring MVC, Spring Boot, Hadoop, d3.js, Velocity.
  \item Achieved real-time data retrieval(delay in less than one second).
  \item 10M level Graph algorithm analysis can be completed in the second level (PageRank 10M point, 120M side iteration five times only 5s).
\end{itemize}

\datedsubsection{\textbf{BUPT} Beijing, China}{2016.4 -- 2016.8}
\role{Graph Processing System}{Individual Projects}
Brief introduction:A pagerank analytics platform using spring boot microservices which combines multiple microservices with a graph processing platform to rank communities of users on Twitter.
\begin{itemize}
  \item Developed a system which used Docker and SpringBoot to build micro services, used Neo4j for storage and Spark GraphX for analysis.
  \item Supports the analytics of a person and its relationship in the social network real-time.
\end{itemize}

\datedsubsection{\textbf{Neo4j Authoritative Guide}}{2016 -- Present} 
\role{Neo4j Authoritative Guide}{Wrote the "Neo4j Authoritative Guide"}
Brief introduction:The first chinese book about Neo4j database. 
\begin{itemize}
  \item Wrote chapter 1 chapter 6 and chapter 8 of the Neo4j Authoritative Guide.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java > Python == C++ == Scala
  \item Platform: Windows, Linux
  \item Web Development: Spring, Spring MVC, Mybatis, Spring Data, Restful, Velocity, HTML, CSS
  \item Database: Mysql, SqlServer, MongoDB, Neo4j, TitanDB
  \item Distributed System: Docker, Spark, Hadoop
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{2} Prize}, China Undergraduate Mathematical Contest in Modeling (CUMCM)}{Sep. 2013}
\datedline{First Class Scholarship， Outstanding Graduates}{2011-2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://zhaobing.me
  \item GitHub: https://github.com/zhaobingcn
  \item Languages: English - Fluent
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
